---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RegDDM

<!-- badges: start -->
<!-- badges: end -->

Build Regression models over Drift Diffusion Model parameters using MCMC! 

## Installation

You can install latest version of RegDDM using Github. The package will later be available on CRAN.

``` r
remotes::install_github("biorabbit/RegDDM")
```

## Example

First, load the package and the example dataset.

```{r example}
library(RegDDM)
data(regddm_data)
```

`data1` is the subject-level dataset with 49 rows and 4 columns:
```{r}
head(regddm_data$data1)
```

`data2` is the subject-level dataset with 6032 rows and 4 columns:
```{r}
head(regddm_data$data2)
```

Specify the model using a list. In this example, we want to study how the memory load of the trial (`memload` variable) influences the drift rate v for each subject differently, and how such influence correlates with the IQ of the subject (`y` variable). Thus, the following model is built:

```{r, cache = TRUE}
model = list(
  v ~ memload,
  y ~ v_0 + v_memload + age + education
)
```

Use the main function to automatically generate the stan model and summary the results. This could take ~20 minutes to run. The rows starting with 'beta_' are the posterior distributions of regression parameters:  

```{r, cache = TRUE, warnings = FALSE}
fit = regddm(
  data1,
  data2,
  model
)
```

In general, higher drift rate will lead to faster and more accurate decision making. 
Increasing memory load has a negative influence on drift rate, which differs by subjects.
Based on the result, The more ”negative” such influence is, the lower the IQ of the
subject. Meanwhile, when experiment condition is neutral, the higher the IQ, the smaller the drift rate.
In other words, subjects with lower IQ are more susceptible to increased memory
load, but they perform better at moderate difficulty.



# Using your own data!
If you want to fit the model on your own data, you need to specify `data1`, `data2` and `model`.

`data1` is subject-level data table. It should contain the following:
* `id`: unique indexing column for each subject. 
* `y`: primary outcome. 
* other covariates that we want to adjust for. These covariates could contain some missing values. However,if there are too many missing values, the model may fail to converge.

`data2` is trial-level data table. It should contain the following:
* `id`: the subject of each trial using the same index in `data1`. All subjects must have a trial and all trials must have a subject.
* `rt`: response time of the trial in seconds.
* `response``: response the trial. must be either 0 or 1. 
* trial-level variables. These are the variables that differ by trial, such as difficulty of the task or different numbers on the screen. We assume that subjects' behavior changes according to these variables. These variables cannot contain missing values.

`model` is the proposed dependency between these parameters. It must be a list containing several formulas, such as `v ~ x1 * x2`
* `a`, `t`, `z`, `v`: can only contain names of trial-level variables in `data2`.
* `y`: can only contain names of covariates in `data1` or parameters specified before in the format of `{a/t/z/v}_trial_level_variables`For example `v_x1` for main effect and `v_x1_x2` for interaction term. 

`family` is the family of distribution of outcome `y`, similar to ones in generalized linear model. It can take either `gaussian`, `bernoulli` or `poisson`. Canonical link function is used in RegDDM.

`ddm_link` specifies the relationship between DDM parameters of each trial and trial-level parameters. By default, 
```{r}
  ddm_link = list(
    a = "exp",
    t = "exp",
    z = "inv_logit",
    v = ""
  )
```

`init` how to initialize the MCMC algorithm. The `"default"` initialization should work in most conditions

`scale` whether to scale the trial-level variables in `data2` or not. If these variables are not scaled, the default prior distribution and constraints will be disabled.

`stan_filename` the file loaction for the automatically generated stan model. If an empty string '' is provided, a temporary file will be created and deleted after the model is fit.



# Citation
to be added





